Efficient ancestry and mutation simulation with msprime 1.0

### 2021-11-27 paper.tex
Add/tweak some citations.

Kingman's coalescent assumes that only two ancestral lineages can merge at
each merger event. Although this is generally a reasonable approximation, there
are certain situations in which the underlying mathematical assumptions are
violated. For example in certain highly fecund organisms
\citep{hedgecock_94,B94,HP11,A04,irwin16}, where individuals have the ability
to produce numbers of offspring on the order of the population size and
therefore a few individuals may produce the bulk of the offspring in any given
generation~\citep{hedgecock_94}. These population dynamics violate basic
assumptions of the Kingman coalescent, and are better modelled by
`multiple-merger' coalescents \citep{DK99,P99,S99,S00,MS01}, in which more than
two lineages can merge in a given event. Multiple-merger coalescent processes
have also been shown to be relevant for modelling the effects of selection on
gene genealogies
\citep{Gillespie909,DS04,desai2013genetic,neher2013genealogies,schweinsberg2017rigorous}.

@@

\section*{Acknowledgements}
We acknowledge the contributions of Ivan Krukov who we consider
eligible for authorship, but were unable to contact for approval.
We would like to thank Iain Mathieson and Alywyn Scally for helpful comments
on the manuscript.
% alphabetised by author. Names spelled out if there's an initial collision
ADK was supported by NIH awards R01GM117241 and R01HG010774.
BE was supported by  DFG grant  273887127 through Priority Programme SPP 1819: Rapid Evolutionary Adaptation (grant STE 325/17-2) to Wolfgang Stephan; BE would also like to acknowledge  funding through The Icelandic Research Centre (Rann{\'i}s) through an Icelandic Research Fund Grant of  Excellence nr.\ 185151-051 to Einar \'Arnason,  Katr\'in Halld\'orsd\'ottir,  Alison Etheridge,  Wolfgang Stephan, and BE.
FB is funded by the Deutsche Forschungsgemeinschaft EXC 2064/1 -- Project number 390727645, and EXC 2124 -- Project number 390838134.
Graham Gower was supported by a Villum Fonden Young Investigator award to Fernando Racimo (project no. 00025300).
Gregor Gorjanc is supported by the Chancellor's Fellowship of the University of Edinburgh and the BBSRC grant to The Roslin Institute BBS/E/D/30002275.
Jere Koskela is supported in part by EPSRC grant EP/R044732/1.
Jerome Kelleher is supported by the Robertson Foundation.
SG acknowledges funding from the Canada Research Chairs Program, from the Canadian Institutes of Health Research PJT 173300, and from the Canadian Foundation for Innovation.

>>>>

Kingman's coalescent assumes that only two ancestral lineages can merge at
each merger event. Although this is generally a reasonable approximation, there
are certain situations in which the underlying mathematical assumptions are
violated. For example in certain highly fecund organisms
\citep{hedgecock_94,B94,HP11,A04,irwin16,vendrami2021sweepstake},
where individuals have the ability
to produce numbers of offspring on the order of the population size and
therefore a few individuals may produce the bulk of the offspring in any given
generation~\citep{hedgecock_94}. These population dynamics violate basic
assumptions of the Kingman coalescent, and are better modelled by
`multiple-merger' coalescents \citep{DK99,P99,S99,S00,MS01}, in which more than
two lineages can merge in a given event. Multiple-merger coalescent processes
have also been shown to be relevant for modelling the effects of selection on
gene genealogies
\citep{Gillespie909,DS04,desai2013genetic,neher2013genealogies,schweinsberg2017rigorous}.

@@

\section*{Acknowledgements}
We acknowledge the contributions of Ivan Krukov who we consider
eligible for authorship, but were unable to contact for approval.
We would like to thank Iain Mathieson and Alywyn Scally for helpful comments
on the manuscript.
% alphabetised by author. Names spelled out if there's an initial collision
ADK was supported by NIH awards R01GM117241 and R01HG010774.
BE was supported by  DFG grant  273887127 through Priority Programme SPP 1819: Rapid Evolutionary Adaptation (grant STE 325/17-2) to Wolfgang Stephan; BE would also like to acknowledge  funding through The Icelandic Research Centre (Rann{\'i}s) through an Icelandic Research Fund Grant of  Excellence nr.\ 185151-051 to Einar \'Arnason,  Katr\'in Halld\'orsd\'ottir,  Alison Etheridge,  Wolfgang Stephan, and BE.
FB is funded by the Deutsche Forschungsgemeinschaft EXC 2064/1 -- Project number 390727645, and EXC 2124 -- Project number 390838134.
GB and KL are supported by an ERC starting grant (ModelGenomLand 757648) to KL.
Graham Gower was supported by a Villum Fonden Young Investigator award to Fernando Racimo (project no. 00025300).
Gregor Gorjanc is supported by the Chancellor's Fellowship of the University of Edinburgh and the BBSRC grant to The Roslin Institute BBS/E/D/30002275.
Jere Koskela is supported in part by EPSRC grant EP/R044732/1.
Jerome Kelleher is supported by the Robertson Foundation.
SG acknowledges funding from the Canada Research Chairs Program, from the Canadian Institutes of Health Research PJT 173300, and from the Canadian Foundation for Innovation.
